A Study on Common Bug Fix Patterns in Rust

### 2022-10-13 sections/related.tex
remove space in cite

% say why pattern-based repair is different from search-based repair -- isn't it sufficient to refer the reader to the survey?
The main intuition in pattern-based program repair methods is that the bug fixing modifications of the programs follow certain patterns. Thus, prior study of the common bug fix patterns is a crucial step for developing these repair tools. Pan et al.~\cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. Martinez and Monperrus~\cite{martinez2015mining, martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that the probabilistic values for repair actions can help with reducing the search space, hence creating a more effective repair tool.

>>>>

% say why pattern-based repair is different from search-based repair -- isn't it sufficient to refer the reader to the survey?
The main intuition in pattern-based program repair methods is that the bug fixing modifications of the programs follow certain patterns. Thus, prior study of the common bug fix patterns is a crucial step for developing these repair tools. Pan et al.~\cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. Martinez and Monperrus~\cite{martinez2015mining,martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that the probabilistic values for repair actions can help with reducing the search space, hence creating a more effective repair tool.
